Articles Of Association

### 2014-11-17 Articles_of_Association_Melbourne_Bitcoin_Technology_Centre_MBTC_2015.tex
WIP: Added General Meeting and supporting points.

  \section*{\centerline{Articles of Association of}}
  \section*{\centerline{BITCOIN TECHNOLOGY CENTERS, INC.}}
  \section*{\centerline{Incorporated in Victoria under the}}
  \section*{\centerline{Associations Incorporation Reform Act 2012}}

@@

@@

% Cover page
% Index page
% Content pages

@@

      \item{} ``\emph{the Act}'' means the Associations Incorporation Reform Act 
      2012 including the Associations Incorporation Reform Regulations 2012;
      \item {}``\emph{address}'' means a postal address or, for the purposes

@@

      \item {}``\emph{officers}'' includes the Board and the Secretary;
      \item {}``\emph{the seal}'' means the common seal of the Association if it

@@

      \item {}``\emph{the Board}'' means the members of the Association so appointed. During any period in which  the    Association is a charity, the Board members are trustees as defined by Section the Charities Act 1997;
      \item {}``\emph{Victoria}'' means the geographic are of Victoria, Australia;

@@

      or by letter;
      \item {}``\emph{electronic communication}'' means the same as in the Electronic Communications Act 2000; and

@@

      \item The name of the incorporated association, such as "XYZ Association Inc".

@@

      \item The purposes of the incorporated association. These explain what the incorporated association is established to do.

@@

      \item State how many general meetings the association must have each year and the period between those meetings. For example, the association may hold a general meeting every four months. The Act only requires an association to hold one general meeting per year, being the annual general meeting. Holding additional general meetings is decided by each association.
      \item Your rules must also provide for the manner in which a general meeting may be called. For example, general meetings may be called by the secretary or the committee or by a specified number or percentage of members giving a request in writing to the secretary to call a general meeting.

@@

      \item - who chairs the meeting
      \item - how voting is conducted (show of hands, secret ballot, casting vote)

>>>>

  \section*{\centerline{Articles of Association of}}
  \section*{\centerline{BITCOIN TECHNOLOGY CENTERS, INC.}}
  \section*{\centerline{Incorporated in Victoria under the}}
  \section*{\centerline{Associations Incorporation Reform Act 2012}}

@@

  \\This material is free and unencumbered material is released into the public domain.
  \\Anyone is free to copy, modify, publish, use, compile, sell, or
  distribute this content, either in source code form or as a compiled
  binary, for any purpose, commercial or non-commercial, and by any
  means.
  \\In jurisdictions that recognize copyright laws, the author or authors
  of this content dedicate any and all copyright interest in the
  material to the public domain. We make this dedication for the benefit
  of the public at large and to the detriment of our heirs and
  successors. We intend this dedication to be an overt act of
  relinquishment in perpetuity of all present and future rights to this
  content under copyright law.
  \\THE MATERIAL IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND,
  EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
  MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT.
  IN NO EVENT SHALL THE AUTHORS BE LIABLE FOR ANY CLAIM, DAMAGES OR
  OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE,
  ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
  OTHER DEALINGS IN THE CONTENTS.
  \\For more information, please refer to http://unlicense.org

@@

% Index page
% Content pages

@@

      \item{} ``\emph{the Act}'' means the Associations Incorporation Reform Act 2012 including the Associations Incorporation Reform Regulations 2012 authored by the State in Victoria;
      \item {}``\emph{Address}'' means a postal address or, for the purposes

@@

      \item {}``\emph{the Committee}'' means the members of the Association so appointed. During any period in which the Association is a charity, the Committee members are trustees as defined by the Charities Act 1997 of Victoria, Australia;
      \item {}``\emph{electronic communication}'' means the same as in the Electronic Communications Act 2000 authored by the State in Victoria;
      \item {}``\emph{Officers}'' includes the Committee and the Secretary;
      \item {}``\emph{the Seal}'' means the common seal of the Association if it

@@

      \item {}``\emph{Victoria}'' means the geographic area of Victoria, Australia;

@@

      or by letter; and

@@

      \item The incorporated association, is to be known as "Bitcoin Technology Centres, Inc." in all holdings.

@@

      \item The purposes of the incorporated association is to promote and assist the adoption and growth of the Bitcoin trading economy and support businesses and consumers embrace digital currency and related technologies and assist our membership to work on building the future of money.

@@

      \item The general meeting of members is the supreme governing body of the Association.
      \item The general meeting is called by the Committee.
      \item The general meeting of members decides on admission and exclusion of members, appoints the committee and decides all matters which are not reserved to other governing bodies of the association.
      \item It supervises the activities of the Comittee and may at any time dismiss the latter without prejudice to any contractual rights of those dismissed.
      \item The right of dismissal exists by law whenever justified by good cause.
      \item General meetings of the Association will be called to order on the 3rd day of each month from February to December each year.
      \item No General meeting will be held in January each year.
      \item The meeting will come to order at 1815 AEST/DST in Melbourne, Victoria.
      \item All meetings will be conducted by live video-conference and recorded, even where all parties to the meeting are present in person.
      \item Live streams of the meeting shall be broadcast and be open and observable to any person without need of any password or other similar technical exclusion mechanism being applied.
      \item Notwithstanding the above, any group of members representing one-fifth of the membership may direct the Comittee to call a general meeting on any date so requested, provided such a request is made in writting and that the date nominated is not less than 16 clear days of delivering instruction to the Commitee c/o the an Address of the Association.
      \item The comittee shall be deemed to be dissolved where it fails to accede to any such properly formed request of the membership and fails to act to call a general meeting and notify the membership within 7 days of the date nominated. Upon dissolution the membership is responsible to call the meeting to order. The first order of business at a general meeting called by members where the Comittee has been dissolved is to appoint a new Comittee by open ballot. Any member permitted by law to do so must be afforded opportunity to nominate to serve on the comittee prior to the ballot at the meeting. 
    \item Annual General Meetings
      \item The Annual General Meeting of the Association shall be held on Hal Finney Day (12th January) each year.
      \item The meeting will come to order at at 1430 in Melbourne, Victoria, Australia.
      \item Annual reports are to be tabled and ratified.
      \item All Officers vacate thier positions at the commencement of the meeting.
      \item The election of a Secretary is the first order of business.
      \item The election of the Comittee is the second order of business.
      \item The outcome of the open ballot is ratified by the membership.
      \item General business (if any) may then be addressed after the new Comittee is ratified.
    \item Resolutions
      \item Resolutions are passed by the general meeting.
      \item The written consent of all members to a proposal is equivalent to a resolution of the general meeting.

@@

      \item All members have equal voting rights at the general meeting.
      \item Resolutions require a majority of the votes of the members present.
      \item Voting is conducted by open ballot with the chair holding a csting vote in the event of a tie.
      \item Resolutions may be taken on matters for which proper notice has not been given only where this is expressly permitted by the articles of association.
      \item Exclusion from voting:
        \item Each member is by law excluded from voting on any resolution concerning a transaction or dispute between him or her, his or her spouse or a lineal relative on the one hand and the association on the other.
